Key Derivation From Noisy Sources With More Errors Than Entropy

### 2014-09-25 constantRate/ConstCompFuzzExt-reorg.tex
editing pass through eurocrypt paper

\begin{abstract}
\lnote{needs work}
Fuzzy extractors convert a noisy source of entropy into the same uniformly distributed key~(Dodis et al., Eurocrypt 2004).  In the process of eliminating noise, they  lose some of the entropy of the original source---in the worst case, as much as the logarithm of the number of tolerated error patterns. For many practical sources, the error tolerance necessary to achieve reliable key derivation is larger than the entropy of the source.  Unfortunately, it is impossible to provide security for every source with this property.  Most known approaches for building fuzzy extractors work in the worst case and thus cannot be used when a source has \emph{more errors than entropy}.

Fortunately, practical sources contain useful structure.  In this work, we exploit distributional structure to construct fuzzy extractors for large classes of noisy sources with more errors than entropy.  
We show an information-theoretic construction and two computational constructions with added features.  Our constructions are for the Hamming metric over symbols of an alphabet.

\begin{itemize} \item \textbf{Information-theoretic}  Our first construction supports sources where each symbol contributes fresh entropy and corrects a constant fraction of Hamming errors over a super-constant size alphabet.

\item \textbf{Computational}
%By adding computational techniques we obtain constructions with additional features.  
Our second construction is also secure when each symbol contributes fresh entropy.  
Additionally, it is a reusable fuzzy extractor~(Boyen, CCS 2004).  A reusable fuzzy extractor allows multiple readings of the source to be enrolled securely.  Our construction is reusable if each individual reading is a supported source.  Previous reusable fuzzy extractors required the correlation between repeated readings to be drawn from a small and unrealistic class.  This construction corrects a sub-constant fraction of errors.  %Computational techniques allow us to show a very sshows that computational assu computationaprovide requires a constant fraction of symbols to have a constant amount of entropy conditioned on prior symbols. It corrects a sub-constant fraction of errors and supports super-constant size alphabets.  In addition, it is first construction of a reusable fuzzy extractor without assumption on the form of errors that occurs between reuse.  This is impossible in the information-theoretic setting for an arbitrary number of reuses~(Boyen, CCS 2004).

@@

\paragraph{Fuzzy Extractors}
Cryptography relies on long-term secrets for key derivation and authentication. However, many sources with sufficient randomness to form long-term secrets provide similar but not identical values at repeated readings~(prominent examples include biometrics and other human-generated data~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password},
physically unclonable functions (PUFs)~\cite{pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical},
and quantum information~\cite{bennett1988privacy}). Turning similar readings into identical values is known as \emph{information reconciliation}; further converting those values into uniformly random secret strings is known as \emph{privacy amplification}~\cite{bennett1988privacy}.
Both of these problems have interactive and non-interactive versions.  In this paper, we are interested in the non-interactive case, which is useful for a single user trying to produce the same key from multiple readings of a physical source at different times.
 A \emph{fuzzy extractor} is the primitive that accomplishes both information reconciliation and privacy amplification non-interactively; fuzzy extractors are defined information-theoretically in~\cite{DBLP:journals/siamcomp/DodisORS08}.

Fuzzy extractors consist of a pair of algorithms: \gen (used once, at ``enrollment'') takes a source value $w$, and produces a key $r$ and a public helper value $p$.  The second algorithm \rep (used subsequently) takes this helper value $p$ and a close $w'$ to reproduce the original key $r$.
The correctness guarantee is that $r$ will be correctly reproduced by \rep as long as $w'$ is no farther than $t$ from $w$ in some metric space.% (in this paper, we focus on the Hamming metric on length $\gamma$ strings over some alphabet $\mathcal{Z}$). \onote{parameters $\gamma$ and $\mathcal{Z}$ are not used until they are reintroduced in our contribution paragraph. Consider ignoring them here.}
 The security guarantee is that $r$ produced by \gen is close to uniform (information-theoretically \cite{DBLP:journals/siamcomp/DodisORS08} or computationally \cite{fuller2013computational}), even given $p$. This guarantee holds as long as $w$ comes from a high-quality distribution, which
traditionally has been defined as \emph{any} distribution with sufficient min-entropy $m$.

@@

Constructions of fuzzy extractors are limited by the tension between security and correctness guarantees: if we allow for higher error tolerance $t$, then we also need higher starting entropy $m$. The reason for this tension is simple: if an adversary who knows $p$ can guess any $w'$ within distance $t$ of $w$, then it will be able to easily obtain the true $r$ by running $\rep$.
%If $t$ is larger, then a single guess for $w'$ may be within distance $t$ of more $w$ values, thus increasing adversarial probability of winning.
In fact, if $t$ is high enough that there are $2^m$ points in a ball of radius $t$, then there exists a distribution of $w$ of min-entropy $m$  \emph{contained entirely in a single ball}.  For this distribution, an adversary can run $\rep$ on the center of this ball and always learn the key $r$.
Thus, if the security guarantee of a given fuzzy extractor holds for \emph{any} source of a given min-entropy $m$ and the correctness guarantees holds for any $t$ errors, then $m$ must   be greater than $\log |B_t|$, where $|B_t|$ denotes the number of points in a ball of radius $t$.  This condition on the source is necessary regardless of whether the fuzzy extractor is information-theoretic or computational, and extends even to the interactive setting.
If a source fails this condition, we will says that it has \emph{more errors than entropy}.

@@

Addtionally, relaxing the security definition to computational will not improve this approach~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}. Thus, we take a different approach and do not attempt to recover $w$.

Our first construction reduces the alphabet size by hashing each input symbol (which comes from a large alphabet) into a much smaller set, so that the resulting hash value has low entropy deficiency.
The intuition behind this approach is that it reduces the size of $B_t$ by reducing the alphabet size, but preserves a sufficient portion of the input entropy.  The resulting string no longer has more errors than entropy.
 We then apply any information-theoretic fuzzy extractor to the resulting string.

@@

\paragraph{The Required Notion of Point Obfuscation} 
Our constructions use simulation-secure  obfuscation of digital lockers, however, we do not require full-fledged virtual black-box obfuscation~\cite{barak2001possibility}. Instead, we rely on the relaxed notion of \emph{virtual grey-box} obfuscation~\cite{bitansky2010strong}. We also require that the obfuscation remains secure even when several digital lockers of correlated points are composed.
Bitanski and Canetti constructed composable digital lockers with virtual grey-box security under particular number-theoretic assumptions~\cite{bitansky2010strong}.

@@

We emphasize that the obfuscation techniques we use are much weaker than general obfuscation, and can be instantiated quite efficiently under appropriate assumptions.

\paragraph{Connection to General Obfuscation}
We note that fuzzy extractors for sources with more errors than entropy can be trivially constructed from virtual grey-box obfuscation for the class of {\em proximity point programs}. A proximity point program $I_w(x)$ tests if $x$ is within distance $t$ of $w$. 
Recently, Bitansky et al.~\cite{BitanskyCKP14} constructed such obfuscation based on the strong assumption of {\em semantically secure graded encodings} \cite{PassTS13}.
The construction of Bitansky et al. is based on multilinear encoding and is  highly impractical.  The obfuscation used in this work can be instantiated quite efficiently under appropriate assumptions.
Additionally, the known obfuscation for proximity point programs is not known to be composable and therefore does not yield a reusable fuzzy extractor.

@@

\begin{definition}[Reusable Fuzzy Extractors]
\label{def:outsider fuzz ext}
Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$.  Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.
Fix some $W_1 \in \mathcal{W}$.  Let $f_2,.., f_q , D$ be a split adversary.  Define the following game for all $i=1,..., q$:
\begin{itemize}%[leftmargin=-.6in]
\item \textbf{Sampling} The challenger samples $w_1\leftarrow W_1$.
\item \textbf{Perturbation} For $i=2,..., q$: the challenger computes $(r_i, p_i)\leftarrow \gen(w_i)$.  Set $w_{i+1} = f_i(w_1, p_1,..., p_i)$.\bnote{should we allow keys to the perturbation adversary?}
\item \textbf{Distinguishing} The advantage of $D$ is
\begin{align*}
\text{Adv}(D)&\overset{def}= \Pr[D(r_1,..., r_{i-1}, r_i, r_{i+1},..., r_q, p_1,..., p_q)=1]\\ &- \Pr[D(r_1,..., r_{i-1}, u, r_{i+1},..., r_q, p_1,..., p_q)=1].
\end{align*}
where $u$ is a uniformly random string.
\end{itemize}
$(\gen, \rep)$ is $(q, s_{sec}, \epsilon_{sec}, f_2,..., f_q)$-reusable if for all $D\in\mathcal{D}_{s_{sec}}$ the advantage is at most $\epsilon_{sec}$.
\end{definition}

@@

\begin{definition}
Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.  In the reusability game above, we say a set of functions $f_2,..., f_q$ are \emph{admissible} if for all $W_1\in \mathcal{W}$ for all $w_1\in W_1$ and $\forall p_1,..., p_q$ that are the public outputs of $\gen$ the implicit distribution $W_{i,w_1,p_1,..., p_{i-1}} = f_i(w_1,p_1,..., p_{i-1})$ is a member of $\mathcal{W}$.
\end{definition}

@@

\begin{construction}
\label{cons:info theoretic}
Let $\mathcal{Z}$ be an alphabet and let $W=W_1,..., W_\gamma$ be a distribution over $\mathcal{Z}^\gamma$.  We describe $\gen, \rep$ as follows:
\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w = w_1,..., w_\gamma$
\item For $j=1,..., \gamma$:
\begin{enumerate}[(i)]
\item Sample $seed_i\leftarrow \zo^d$.
\item Set $v_i = \cond(w_i, seed_i)$.
\end{enumerate}
\item Set $(r, p') \leftarrow \gen(v_1,..., v_\gamma)$.
\item Set $p = (p', seed_1,..., seed_\gamma)$.
\item Output $(r, p)$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rep}
\begin{enumerate}
\item \underline{Input}: $(w', p = (p', seed_1,..., seed_\gamma))$
\item For $j=1,..., \gamma$:
\begin{enumerate}[(i)]
\item Set $v_i = \cond(w_i, seed_i)$.
\end{enumerate}
\item Output $r = \rep'(v', ss)$.
\end{enumerate}
\vspace{0.7in}
\end{minipage}
\end{tabular}
\end{center}
\end{construction}

@@

In this section we show that \consref{cons:info theoretic} supports partial block sources with more errors than entropy.  The required entropy of partial block source is $\alpha (\gamma-\beta ) = \Theta(\gamma)$.  The condenser of Dodis et al~\cite{dodis2014key} has a constant entropy loss, so $\alpha-\tilde{\alpha} = \Theta(1)$. This means that the input entropy to the fuzzy extractor is $\Theta(\gamma)$.   We assume that the new alphabet $\mathcal{Y}$ is of constant size.  Standard fuzzy extractors on constant size alphabets correct a constant fraction of errors at a entropy loss of $\Theta(\gamma)$, yielding $\kappa = \Theta(\gamma)$.  Thus, our construction is secure for distributions with more errors than entropy whenever $|\mathcal{Z}| = \omega(1)$.
More formally:
\[
\text{\# Errors} - \text{Entropy} = \log |B_t| - \Hoo(W) <  t \log |\mathcal{Z}| - \Theta(\gamma)-= \Theta(\gamma) \log |\mathcal{Z}| - \Theta(\gamma)  > 0
\]
That is, there exists a super-constant alphabet size for which \consref{cons:info theoretic} is secure with more errors than entropy.

@@

\noindent
%There are three main differences between this construction and \consref{cons:first construction}.  They are as follows:
%\begin{itemize}
%\item Multiple blocks are concatenated together.  This comes at a cost to error tolerance but allows us to significant decrease the required entropy in each block.  This paradigm is similar to \emph{sample-then-extract} from the locally computable extractors literature~\cite{lu2002hyper,vadhan2003constructing}.  For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.
%\item Instead of encoding a bit of the key with each obfuscated value we encode the entire key with each obfuscated value.  This requires the use of digital lockers in place of point obfuscations.  Instead of having to open ``most'' of the obfuscations, it is only necessary for us to open a single obfuscation.  \consref{cons:first construction} only hid part of the key in each obfuscation.  This allowed some blocks in the distribution to be ``weak.''  However, sampling smoothes out $W$ so that all $V_i$ are ``good'' simultaneously.
%\item \consref{cons:first construction} required a large alphabet as blocks were individually obfuscated.  This construction works for an arbitrary size alphabet.  We show it supports $\Huse (W)\le 0$ when the alphabet size is super-constant in the security parameter.
%\end{itemize}
The use of a computational primitive~(obfuscation) allows us to sample multiple times, because we need to argue only about individual entropy of $V_i$, as opposed to the information-theoretic setting, where it would be necessary to argue about the entropy of the joint variable $V$.  This is the property that allows reusability.

@@

\subsection{Security of \consref{cons:sampling}}
\label{ssec:sec cons sampling}
In this section we outline security of \consref{cons:sampling}.  A proof of security appears in\apref{sec:analysis sampling}.
With overwhelming probability, at each of the $\ell$ iterations, the sampler will choose enough coordinates of $W$ that have high entropy, making $V_i$ have sufficient entropy.   Once each of the $V_1,..., V_\ell$ have high entropy the obfuscations are unlikely to return a value other than $\perp$ to an adversary.
% forms a block-unguessable distribution.  Then security essentially follows from the security of \consref{cons:first construction}. %follows very similarly to \lemref{lem:security of cons}~(used to show security of \consref{cons:first construction}).
%Essentially, the argument is that an adversary will never be able to open a digital locker and thus they learn no information about the key.  %By the same argument of Then \consref{cons:sampling} is just \consref{cons:first construction} applied to $V_1,.., V_\ell$, and security follows by \lemref{lem:security of cons}.
We begin by showing that each $V_i$ is statistically close to a high entropy distribution.   Let $\Lambda$ represent the random variable of all the coins used by $\sample$ and $\lambda=\lambda_1 \dots \lambda_\ell$
be some particular outcome.

@@

\subsection{More errors than entropy?}
In this section, we show when \consref{cons:sampling} supports partial block sources with more errors than entropy.  The required entropy of partial block source is $\alpha (\gamma-\beta ) = \Theta(\gamma)$.  We are able to correct $o(\gamma)$ errors.
This yields:
\[
\text{\# Errors} - \text{Entropy} =  \log |B_t| -\Hoo(W) < t \log |\mathcal{Z}| - \Theta(\gamma)= o(\gamma) \log |\mathcal{Z}| - \Theta(\gamma)
\]
That is, there exists a super-constant alphabet size for which \consref{cons:sampling} is secure with more errors than entropy.

\textbf{Note:} \consref{cons:sampling} works for an arbitrary size alphabet; however, for a constant size alphabet, the required entropy is greater than the number of corrected error patterns.  However, \consref{cons:sampling} is reusability for an arbitrary size alphabet.

\section{Allowing Correlated Symbols}
\label{sec:cor construction}
In the previous two sections, we presented constructions that supported restricted classes of distributions with more errors than entropy.  Unfortunately, both Constructions~\ref{cons:info theoretic} and \ref{cons:sampling} required each symbol to contribute ``fresh'' entropy.  In this section, we present a computational construction that allows for correlation between symbols while still supporting more errors than entropy and correcting a constant fraction of errors.
This construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.

Before presenting the construction we provide some definitions from error correcting codes.
We use slightly nonstandard error-correct codes over $\{0,1\}^\gamma$, which correct up to $t$ bit flips from $0$ to $1$ but no bit flips from $1$ to $0$ (this is the Hamming analog of the $Z$-channel~\cite{tallini2002capacity}).\footnote{Any code that corrects $t$ Hamming errors also corrects $t$ $0\rightarrow 1$ errors, but more efficient codes  exist for this type of error~\cite{tallini2002capacity}.
Codes with $2^{\Theta(\gamma)}$ codewords and $t = \Theta(\gamma)$ over the binary alphabet exist for Hamming errors and suffice for our purposes~(first constructed by Justensen~\cite{justesen1972class}).  These codes also yield a constant error tolerance for $0\rightarrow 1$ bit flips.
The class of errors we support in our source~($t$ Hamming errors over a large alphabet) and the class of errors for which we need codes~($t$ $0\rightarrow 1$ errors) are different.
}
\begin{definition}
\label{def:hamming z channel}
For a point $c\in \zo^\gamma$ define $\neigh_t(c) $ as the set of all points where at most $t$ bits $c_i$ are changed from $0$ to $1$.
\end{definition}

@@

We adapt the definition of Boyen to the computational setting~(\defref{def:outsider fuzz ext}).  
The definition of Boyen considers a single adversary.  We split the adversary into two parts, one of which is information-theoretic and another that is computationally bounded.  The functions $f_2,..., f_q$ can be thought of as a single adversary that sees all prior state.  However, to provide meaningful security in the computational setting, we cannot have communication between these adversaries.\footnote{An alternative would be to have a single computationally bounded adversary.  Our construction satisfies this alternative adaption as well.}
Because these two adversaries do not communicate we strengthen the definition by allowing the perturbation adversary~($f_i$) to see the original sample $w_1$.  This was not allowed in the definition of Boyen as it would make security impossible.

>>>>

\begin{abstract}
\lnote{needs work}
Fuzzy extractors convert repeated readings of a noisy source of entropy into the same uniformly distributed key~(Dodis et al., Eurocrypt 2004).  In the process of eliminating noise, they  lose some of the entropy of the original source---in the worst case, as much as the logarithm of the number of tolerated error patterns. For many practical sources, the error tolerance necessary to achieve reliable key derivation is larger than the entropy of the source.  Unfortunately, it is impossible to provide security for every source with this property.  Most known approaches for building fuzzy extractors work in the worst case and thus cannot be used when a source has \emph{more errors than entropy}.

Fortunately, practical sources contain useful structure.  In this work, we exploit distributional structure to construct fuzzy extractors for large classes of noisy sources with more errors than entropy.  
We show an information-theoretic construction and two computational constructions with additional features.  Our constructions are for the Hamming metric.

\begin{itemize} \item \textbf{Information-theoretic}  Our first construction supports sources where each symbol contributes fresh entropy and corrects a constant fraction of errors over a super constant size alphabet.

\item \textbf{Computational}
%By adding computational techniques we obtain constructions with additional features.  
Our second construction is also secure when each symbol contributes fresh entropy.  
Additionally, it is a reusable fuzzy extractor~(Boyen, CCS 2004).  A reusable fuzzy extractor allows multiple readings of the source to be enrolled securely.  Our construction is reusable if each individual reading is a supported source.  Previous reusable fuzzy extractors required the correlation between repeated readings to be drawn from a small and unrealistic class.  This construction corrects a sub-constant fraction of errors over a super constant size alphabet.  %Computational techniques allow us to show a very sshows that computational assu computationaprovide requires a constant fraction of symbols to have a constant amount of entropy conditioned on prior symbols. It corrects a sub-constant fraction of errors and supports super-constant size alphabets.  In addition, it is first construction of a reusable fuzzy extractor without assumption on the form of errors that occurs between reuse.  This is impossible in the information-theoretic setting for an arbitrary number of reuses~(Boyen, CCS 2004).

@@

\paragraph{Fuzzy Extractors}
Cryptography relies on long-term secrets for key derivation and authentication. However, many sources with sufficient randomness to form long-term secrets provide similar but not identical values at repeated readings. Prominent examples include biometrics and other human-generated data~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password},
physically unclonable functions (PUFs)~\cite{pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical},
and quantum information~\cite{bennett1988privacy}. Turning similar readings into identical values is known as \emph{information reconciliation}; further converting those values into uniformly random secret strings is known as \emph{privacy amplification}~\cite{bennett1988privacy}.
Both of these problems have interactive and non-interactive versions.  In this paper, we are interested in the non-interactive case, which is useful for a single user trying to produce the same key from multiple readings of a physical source at different times.
 A \emph{fuzzy extractor} is the primitive that accomplishes both information reconciliation and privacy amplification non-interactively; fuzzy extractors are defined in~\cite{DBLP:journals/siamcomp/DodisORS08}.

Fuzzy extractors consist of a pair of algorithms: \gen (used once, at ``enrollment'') takes a source value $w$, and produces a key $r$ and a public helper value $p$.  The second algorithm \rep (used subsequently) takes this helper value $p$ and a close $w'$ to reproduce the original key $r$.
The correctness guarantee is that $r$ will be correctly reproduced by \rep as long as $w'$ is no farther than $t$ from $w$ in some metric space. In this work, we consider the Hamming metric.
 The security guarantee is that $r$ produced by \gen is close to uniform (information-theoretically \cite{DBLP:journals/siamcomp/DodisORS08} or computationally \cite{fuller2013computational}), even given $p$. This guarantee holds as long as $w$ comes from a high-quality distribution, which
traditionally has been defined as \emph{any} distribution with sufficient min-entropy $m$.

@@

Constructions of fuzzy extractors are limited by the tension between security and correctness guarantees: if we allow for higher error tolerance $t$, then we also need higher starting entropy $m$. The reason for this tension is simple: if an adversary who knows $p$ can guess some $w'$ within distance $t$ of $w$, then it will be able to easily obtain the true $r$ by running $\rep$.
%If $t$ is larger, then a single guess for $w'$ may be within distance $t$ of more $w$ values, thus increasing adversarial probability of winning.
In fact, if $t$ is high enough that there are $2^m$ points in a ball of radius $t$, then there exists a distribution of $w$ of min-entropy $m$  \emph{contained entirely in a single ball}.  For this distribution, an adversary can run $\rep$ on the center of this ball and always learn the key $r$.
Thus, if the security guarantee of a given fuzzy extractor holds for \emph{any} source of a given min-entropy $m$ and the correctness guarantees holds for any $t$ errors, then $m$ must   be greater than $\log |B_t|$, where $|B_t|$ denotes the number of points in a ball of radius $t$.  This condition on the source holds regardless of whether the fuzzy extractor is information-theoretic or computational, and extends even to the interactive setting.
If a source fails this condition, we will says that it has \emph{more errors than entropy}.

@@

Additionally, computational definitions of security suffer from similar problems~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}. Thus, we take a different approach and do not attempt to recover $w$.

Our first construction reduces the alphabet size by hashing each input symbol (which comes from a large alphabet) into a much smaller set, so that the resulting hash value has low entropy deficiency.
The intuition behind this approach is that it reduces the size of $B_t$ by reducing the alphabet size, but preserves a sufficient portion of the input entropy.  The resulting string no longer has more errors than entropy.
 We then apply an information-theoretic fuzzy extractor to the resulting string.

@@

\paragraph{The Required Notion of Obfuscation} 
Our constructions use simulation-secure  obfuscation of digital lockers, however, we do not require full-fledged virtual black-box obfuscation~\cite{barak2001possibility}. Instead, we rely on the relaxed notion of \emph{virtual grey-box} obfuscation~\cite{bitansky2010strong}. We also require that the obfuscation remains secure even when several digital lockers of correlated points are composed.
Bitanski and Canetti constructed composable digital lockers with virtual grey-box security under particular number-theoretic assumptions~\cite{bitansky2010strong}.

@@

\paragraph{Connection to General Obfuscation}
We note that fuzzy extractors for sources with more errors than entropy can be trivially constructed from virtual grey-box obfuscation for the class of {\em proximity point programs}. A proximity point program $I_w(x)$ tests if $x$ is within distance $t$ of $w$. 
Recently, Bitansky et al.~\cite{BitanskyCKP14} constructed such obfuscation based on the strong assumption of {\em semantically secure graded encodings} \cite{PassTS13}.
The construction of Bitansky et al. is based on multilinear encoding and is  highly impractical.  Our constructions use obfuscated digital lockers.  Obfuscated digital lockers are instantiable under significant weaker assumptions and can be implemented quite efficiently.
\bnote{we need to say we are weaker than general obfuscation.  happy with this? merged with sentence from above}
Additionally, the known obfuscation for proximity point programs is not known to be composable and therefore does not yield a reusable fuzzy extractor.

@@

\begin{definition}[Reusable Fuzzy Extractors]
\label{def:outsider fuzz ext}
Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$.  Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.
Fix some $W_1 \in \mathcal{W}$.  Let $f_2,.., f_q , D$ be a split adversary.  Define the following game for all $i=1,..., q$:
\begin{itemize}%[leftmargin=-.6in]
\item \textbf{Sampling} The challenger samples $w_1\leftarrow W_1, u\leftarrow \zo^\kappa$.
\item \textbf{Perturbation} For $i=2,..., q$: the challenger computes $(r_i, p_i)\leftarrow \gen(w_i)$.  Set $w_{i+1} = f_i(w_1, p_1,..., p_i)$.\bnote{should we allow keys to the perturbation adversary?}
\item \textbf{Distinguishing} The advantage of $D$ is
\begin{align*}
\text{Adv}(D)&\overset{def}= \Pr[D(r_1,..., r_{i-1}, r_i, r_{i+1},..., r_q, p_1,..., p_q)=1]\\ &- \Pr[D(r_1,..., r_{i-1}, u, r_{i+1},..., r_q, p_1,..., p_q)=1].
\end{align*}
\end{itemize}
$(\gen, \rep)$ is $(q, s_{sec}, \epsilon_{sec}, f_2,..., f_q)$-reusable if for all $D\in\mathcal{D}_{s_{sec}}$ the advantage is at most $\epsilon_{sec}$.
\end{definition}

@@

\begin{definition}
Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.  In the reusability game above, we say a set of functions $f_2,..., f_q$ are \emph{admissible} if for all $W_1\in \mathcal{W}$ for all $w_1\in W_1$ and $\forall p_1,..., p_q$ that are the public outputs of $\gen$ the distribution $W_{i,w_1,p_1,..., p_{i-1}} = f_i(w_1,p_1,..., p_{i-1})$ is a member of $\mathcal{W}$.
\end{definition}

@@

\begin{construction}
\label{cons:info theoretic}
Let $\mathcal{Z}$ be an alphabet and let $W=W_1,..., W_\gamma$ be a distribution over $\mathcal{Z}^\gamma$.  We describe $\gen, \rep$ as follows:
\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w = w_1,..., w_\gamma$
\item For $j=1,..., \gamma$:
\begin{enumerate}[(i)]
\item Sample $seed_i\leftarrow \zo^d$.
\item Set $v_i = \cond(w_i, seed_i)$.
\end{enumerate}
\item Set $(r, p') \leftarrow \gen'(v_1,..., v_\gamma)$.
\item Set $p = (p', seed_1,..., seed_\gamma)$.
\item Output $(r, p)$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rep}
\begin{enumerate}
\item \underline{Input}: $(w', p = (p', seed_1,..., seed_\gamma))$
\item For $j=1,..., \gamma$:
\begin{enumerate}[(i)]
\item Set $v_i = \cond(w_i, seed_i)$.
\end{enumerate}
\item Output $r = \rep'(v', ss)$.
\end{enumerate}
\vspace{0.7in}
\end{minipage}
\end{tabular}
\end{center}
\end{construction}

@@

In this section we show that \consref{cons:info theoretic} supports partial block sources with more errors than entropy.  The structure of a partial block source implies that  $\Hoo(W) \ge \alpha (\gamma-\beta ) = \Theta(\gamma)$.  We assume that $\Hoo(W) = \Theta(\gamma)$. The condenser of Dodis et al~\cite{dodis2014key} has a constant entropy loss, so $\alpha-\tilde{\alpha} = \Theta(1)$. This means that the input entropy to the fuzzy extractor is $\Theta(\gamma)$.   We assume that the new alphabet $\mathcal{Y}$ is of constant size.  Standard fuzzy extractors on constant size alphabets correct a constant fraction of errors at a entropy loss of $\Theta(\gamma)$, yielding $\kappa = \Theta(\gamma)$.  Thus, our construction is secure for distributions with more errors than entropy whenever $|\mathcal{Z}| = \omega(1)$.
More formally:
\[
\text{\# Errors} - \text{Entropy} = \log |B_t| - \Hoo(W) \ge  t \log |\mathcal{Z}| - \Theta(\gamma)-= \Theta(\gamma) \log |\mathcal{Z}| - \Theta(\gamma)  > 0
\]
That is, there exists a super-constant alphabet size for which \consref{cons:info theoretic} is secure with more errors than entropy.

@@

\noindent
%There are three main differences between this construction and \consref{cons:first construction}.  They are as follows:
%\begin{itemize}
%\item Multiple blocks are concatenated together.  This comes at a cost to error tolerance but allows us to significant decrease the required entropy in each block.  This paradigm is similar to \emph{sample-then-extract} from the locally computable extractors literature~\cite{lu2002hyper,vadhan2003constructing}.  For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.
%\item Instead of encoding a bit of the key with each obfuscated value we encode the entire key with each obfuscated value.  This requires the use of digital lockers in place of point obfuscations.  Instead of having to open ``most'' of the obfuscations, it is only necessary for us to open a single obfuscation.  \consref{cons:first construction} only hid part of the key in each obfuscation.  This allowed some blocks in the distribution to be ``weak.''  However, sampling smoothes out $W$ so that all $V_i$ are ``good'' simultaneously.
%\item \consref{cons:first construction} required a large alphabet as blocks were individually obfuscated.  This construction works for an arbitrary size alphabet.  We show it supports $\Huse (W)\le 0$ when the alphabet size is super-constant in the security parameter.
%\end{itemize}
The use of a computational primitive~(obfuscation of digital lockers) allows us to sample multiple times, because we need to argue only about individual entropy of $V_i$, as opposed to the information-theoretic setting, where it would be necessary to argue about the entropy of the joint variable $V$.  This is the property that allows reusability.

@@

\subsection{Security of \consref{cons:sampling}}
\label{ssec:sec cons sampling}
In this section we outline security of \consref{cons:sampling}.  A proof of security appears in \apref{sec:analysis sampling}.
With overwhelming probability, at each of the $\ell$ iterations, the sampler will choose enough coordinates of $W$ that have high entropy, making $V_i$ have sufficient entropy.   Once each of the $V_1,..., V_\ell$ have high entropy the obfuscations are unlikely to return a value other than $\perp$ to an adversary.
% forms a block-unguessable distribution.  Then security essentially follows from the security of \consref{cons:first construction}. %follows very similarly to \lemref{lem:security of cons}~(used to show security of \consref{cons:first construction}).
%Essentially, the argument is that an adversary will never be able to open a digital locker and thus they learn no information about the key.  %By the same argument of Then \consref{cons:sampling} is just \consref{cons:first construction} applied to $V_1,.., V_\ell$, and security follows by \lemref{lem:security of cons}.
We begin by showing that each $V_i$ is statistically close to a high entropy distribution.   Let $\Lambda$ represent the random variable of all the coins used by $\sample$ and $\lambda=\lambda_1 \dots \lambda_\ell$
be some particular outcome.

@@

\subsection{More errors than entropy?}
In this section, we show when \consref{cons:sampling} supports partial block sources with more errors than entropy.  The structure of the partial block source implies that $\Hoo(W) \ge \alpha (\gamma-\beta ) = \Theta(\gamma)$.  We assume that $\Hoo(W) = \Theta(\gamma)$.  We are able to correct $o(\gamma)$ errors.
This yields:
\[
\text{\# Errors} - \text{Entropy} =  \log |B_t| -\Hoo(W) \ge t \log |\mathcal{Z}| - \Theta(\gamma)= o(\gamma) \log |\mathcal{Z}| - \Theta(\gamma)
\]
That is, there exists a super-constant alphabet size for which \consref{cons:sampling} is secure with more errors than entropy.

\textbf{Notes:} \consref{cons:sampling} works for an arbitrary size alphabet; however, for a constant size alphabet, the required entropy is greater than the number of corrected error patterns.  However, \consref{cons:sampling} is reusability for an arbitrary size alphabet.

Furthermore, we showed that \consref{cons:sampling} is secure on partial block sources.  In fact, it is secure for any source where sampling produces a high entropy string~($\omega(\log n)$) with overwhelming probability.  For comparison with \consref{cons:info theoretic} we restrict our attention to partial block sources.\bnote{I just added this.  Okay?}

\section{Allowing Correlated Symbols}
\label{sec:cor construction}
In the previous two sections, we presented constructions that supported restricted classes of distributions with more errors than entropy.  Unfortunately, both Constructions~\ref{cons:info theoretic} and \ref{cons:sampling} required each symbol to contribute ``fresh'' entropy.  In this section, we present a computational construction that allows for correlation between symbols while still supporting more errors than entropy and correcting a constant fraction of errors.
This construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.  Instead of having large parts of the string $w$ unlock $r$, we have individual symbols unlock bits of $r$.

Before presenting the construction we provide some definitions from error correcting codes.
We use error-correct codes over $\{0,1\}^\gamma$ which correct up to $t$ bit flips from $0$ to $1$ but no bit flips from $1$ to $0$ (this is the Hamming analog of the $Z$-channel~\cite{tallini2002capacity}).\footnote{Any code that corrects $t$ Hamming errors also corrects $t$ $0\rightarrow 1$ errors, but more efficient codes  exist for this type of error~\cite{tallini2002capacity}.
Codes with $2^{\Theta(\gamma)}$ codewords and $t = \Theta(\gamma)$ over the binary alphabet exist for Hamming errors and suffice for our purposes~(first constructed by Justensen~\cite{justesen1972class}).  These codes also yield a constant error tolerance for $0\rightarrow 1$ bit flips.
The class of errors we support in our source~($t$ Hamming errors over a large alphabet) and the class of errors for which we need codes~($t$ $0\rightarrow 1$ errors) are different.
}
\begin{definition}
\label{def:hamming z channel}
For a point $c\in \zo^\gamma$ define $\neigh_t(c) $ as the set of all points where at most $t$ bits $c_i$ are changed from $0$ to $1$.
\end{definition}

@@

We adapt the definition of Boyen to the computational setting~(\defref{def:outsider fuzz ext}).  
The definition of Boyen considers a single adversary.  We split the adversary into two parts, one of which is information-theoretic and another that is computationally bounded.  The functions $f_2,..., f_q$ can be thought of as a single adversary that sees all prior state.  However, to provide meaningful security in the computational setting, we cannot have communication between these adversaries.\footnote{An alternative would be to have a single computationally bounded adversary.  \consref{cons:sampling} satisfies this alternative adaption as well.}
Because these two adversaries do not communicate we strengthen the definition by allowing the perturbation functions,  $f_i$, to see the original sample $w_1$.  This was not allowed in the definition of Boyen as it would make security impossible.
